---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# countess: Helpers for "dplyr"'s "count" Function

Convenience functions built on top of dplyr to count the number of instances of
each value in columns of data frames.

- `count_all()` is `group_by_all()` plus `tally()`. 
- `count_at()` is `group_by_at()` plus `tally()`. 
- `count_if()` is `group_by_if()` plus `tally()`. 

## Installation

You can install this development version of countess using

``` r
# install.packages("remotes")
remotes::install_github("richierocks/countess")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r loadplyr, echo = FALSE}
suppressPackageStartupMessages(library(dplyr))
set.seed(19790801)
```

```{r counts}
library(dplyr)
library(countess)
n <- 100
quarks <- data_frame(
  first_gen = sample(c("up", "down"), n, replace = TRUE),
  second_gen = sample(c("charm", "strange"), n, replace = TRUE),
  third_gen = factor(sample(c("top", "bottom"), n, replace = TRUE))
)
quarks %>% count_all()
quarks %>% count_at(vars(contains("ir")))
quarks %>% count_if(is.factor)
```
